Increasing User Engagement in a Volunteer-Based Ephemeral Evolutionary Computation System

### 2017-11-09 2017-EUROPAR/Gamification/paper.tex
Please add this data
@mariosky I think it's important that we enphasize that the registered
users contribute, per person, much more than non-registereed ones.
Check out the last comment
Basically use also statistical measures to compare both, @mariosky. Do
you have the data handy?

\begin{table}[h!tbp]
  \small
  \caption{ Log file record structure}
  \label{tab:record}
  \centering
  \small
  \begin{tabular}{l  l}
    \hline\noalign{\smallskip}
    Attribute & Value \\
    \noalign{\smallskip}\hline\noalign{\smallskip}
    chromosome   & The individual sent to the server as a string of 160 bits.  \\ \hline
    fitness & fitness as an integer.  \\ \hline
    IP & IP address of the participant (later anonymized) .\\ \hline
    user & user-name or the string `anonymous'.  \\ \hline
    worker\_uuid & unique identifier of the HTTP Worker that sent the participation.   \\ \hline
    level &  level of user or the string `info' \\ \hline
    message & Only PUT messages were recorded in this experiment. \\ \hline
    timestamp & A time-stamp based on the Unix epoch\\ \hline
  \end{tabular}
\end{table}
%
At the end of the experiment the resulting log file (whose fields are shown in Table \ref{tab:record}) contained 933,513 contributions both
registered users and anonymous volunteers. Registered users were responsible of around
90\% of the contributions. The JSON data recorded for each contribution is  presented
in Table~\ref{tab:record}.

\begin{figure}[h!tbp]
    \centering
        \includegraphics[width=0.9\linewidth]{img/puts_user.png}
        \includegraphics[width=0.9\linewidth]{img/puts_ip.png}
    \caption{Usage by registered (left) and anonymous (right) users.  Users are ranked by
        the number of requests sent, in the \emph{x} axis is the rank, and in the \emph{y} axis
        number or PUTs in a logarithmic scale.}
    \label{fig:puts}
\end{figure}
%
Contributions are expressed as the number of HTTP PUT requests sent to the server. In Figure~\ref{fig:puts} a comparison between the contribution of registered vs anonymous users is
presented. There were only 18 registered users, and the exact number of anonymous
is not known as we only recorded the IP of the request, also a registered users
could sometimes be anonymous too, this could be because the first time they visit
the application they automatically begin to work as anonymous. Nevertheless,
there were 91 distinct IPs that had `anonymous' as the user. In the plot of
anonymous users, some of the last in the rank could in fact be registered users,
momentarily participating as anonymous. Even if this is not considered, only
about 16\% of users attending the call decided to participate as named users.

There is a notable difference in the amount of participation between the two
groups, and also in the slope of the plot.

>>>>

\begin{table}[h!tbp]
  \small
  \caption{ Log file record structure}
  \label{tab:record}
  \centering
  \small
  \begin{tabular}{l  l}
    \hline\noalign{\smallskip}
    Attribute & Value \\
    \noalign{\smallskip}\hline\noalign{\smallskip}
    chromosome   & The individual sent to the server as a string of 160 bits.  \\ \hline
    fitness & fitness as an integer.  \\ \hline
    IP & IP address of the participant (later anonymized) .\\ \hline
    user & user-name or the string `anonymous'.  \\ \hline
    worker\_uuid & unique identifier of the HTTP Worker that sent the participation.   \\ \hline
    level &  level of user or the string `info' \\ \hline
    message & Only PUT messages were recorded in this experiment. \\ \hline
    timestamp & A time-stamp based on the Unix epoch\\ \hline
  \end{tabular}
\end{table}
%
At the end of the experiment the resulting log file (whose fields are shown in Table \ref{tab:record}) contained 933,513 contributions both
registered users and anonymous volunteers. Registered users were responsible for about
90\% of the contributions. % While being only x% of the total number
                           % of unique users - JJ
The JSON data recorded for each contribution is  presented
in Table~\ref{tab:record}.

\begin{figure}[h!tb]
    \centering
        \includegraphics[width=0.9\linewidth]{img/puts_user.png}
        \includegraphics[width=0.9\linewidth]{img/puts_ip.png}
    \caption{Usage by registered (top) and anonymous (bottom) users.  Users are ranked by
        the number of requests sent, in the \emph{x} axis is the rank, and in the \emph{y} axis
        number or PUTs in a logarithmic scale.}
      \label{fig:puts}
% Maybe we should scale dividing by number of users and put them
% together. - JJ
\end{figure}
%
Contributions are expressed as the number of HTTP {\tt PUT} requests
sent to the server. In Figure~\ref{fig:puts} a comparison between the
contribution of registered vs anonymous users is 
presented.

The first observation arises from the length of the $x$ axis. There
were only 18 registered users vs 91 distinct IPs; the 
exact number of anonymous users is upper-bounded by that amount but is
not known precisely as we only recorded the IP of the request, we did
not use cookies or other means of identification since it was not
actually needed for the experiment. Besides, a registered user
could sometimes be anonymous too, which could be caused by the fact that the first time they visited
the application they automatically begin to work as anonymous, so the
number of non-anonymous users, 91, is actually the amount of unique
IPs that had `anonymous' as the user. In the plot of 
anonymous users, some of the last in the rank could in fact be registered users,
momentarily participating as anonymous. Even if this is not considered, only
about 16\% of users attending the call decided to participate as named
users and thus enter the game dynamics.

The second observation is apparent in the $y$ axis of Figure
\ref{fig:puts}. There is a notable difference in the amount of
participation between the two groups, and also in the slope of the
plot. %Maybe a statistical comparison? Median, for instance - JJ
